Mapping Microblog Posts to Encyclopedia Articles

### 2011-03-14 lids/twittersearchwrap/paper/paper.tex
rewrote abstract and intro

\title{Mapping Microblog Posts to Encyclopedia Articles}
\author{Uta L\"{o}sch \and David M\"{u}ller \and Andreas Harth}
\institute{
	Karlsruhe Institute of Technology (KIT), D-76131 Karlsruhe, Germany\\ 
	\email{uta.loesch@kit.edu},\\
	\email{david.mueller@student.kit.edu},\\
	\email{harth@kit.edu}
}
\begin{document}

@@

\begin{abstract}
Microblog messages contain so-called hashtags which are usedto mark keywords or topics. To facilitate understanding the meaning of a hashtag in the context of microblog, we have developed a system which annotates hashtags based on Twitter search results with encyclopedia entities that best describe the hashtag, thus offering means of quickly grasping the meaning of the hashtag and relating the hashtags to external content, thus providing starting points for further exploration of the hashtags' context. In an evaluation we analyse the stability of the related entities.
\end{abstract}

Keywords: Twitter, Wikipedia, DBpedia, RDF

\nop{
http://tagdef.com/ has a list of popular tags
}

@@

Microblogging has become more and more popular over the last years, especially with the most prominent and most widely used microblogging platform Twitter\footnote{\url{http://twitter.com}} which has become very influential over the last years. The idea of micro-blogs is the same as that of blogs, except that the message length is restricted, in the case of Twitter the restriction is 140 characters. Twitter has a total of about 190 million of users who produce 65 million Twitter messages a day. Thus, Twitter represents a huge data source on the web.

On microblogging platforms it is possible to search for messages containing a specific hashtag. This search returns a fixed number of most recent messages containing the tag. However, it is hard to grasp the context of the results and to get further information on the topic that was searched for. As each single microblog post is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.

To facilitate this putting into context of the search results, we propose to annotate search results with a set of entities which reflect the content of the result feeds. These entities will not only help to understand the search terms, but also serve as a starting point for refining the search or searching for further information related to the search result.

Furthermore, this annotation will help to understand hashtags. Hash tags are frequently used to associate messages with a specific topic, place, person or event on microblogging platforms. For example, messages talking about what is going on at the European Semantic Web Conference 2011 will frequently be tagged with $\#eswc2011$. If users encounter this hashtag and do not understand it, they can search for it on the microblogging platform. However, understanding a search result is difficult and time-consuming. Using our approach the search will not only return messages using the tag but also a set of entities which have been detected in the search result. These entities will help the user to gain an understanding in which context the hashtag is used and what it may mean. If a hashtag can be associated with an entity with high confidence, the entity can be seen as descriptive for the hashtag. A system may be envisioned which automatically finds entitities which are equivalent to a hashtag. Thus, these hashtag-entity pairs may be used similarly to systems in which hashtags can be defined manually, such as is possible on \#tagdef\footnote{\url{http://www.tagdef.com}}.

Finding entities matching a query, especially a query for a given hashtag is difficult as little context is available due to the short length of each single message. Additional problems are due to synonyms and homonyms in the set of hashtags that are frequently used. For example, both the hashtags $\#ka$ and $\#karlsruhe$ are frequently used when talking about topics which are related to the city Karlsruhe. The tag $\#ka$ is however also used in the context of the car type Ford Ka. Thus, when searching for $\#ka$ on a microblogging platform, messages relating to Karlsruhe will be found as well as messages related to Ford Ka. An approach which aims at finding relevant entities for a given search will have to be able to deal with these problems.

In this paper, we present a system which automatically annotates a microblog search result with encyclopedia entities. While it would be more interesting to annotate each single microblog message with relevant entities, microblog messages are too short to contain much relevant information which could be used as input for an annotation tool such as the Wikifier \cite{key:wikifier}. Thus, we chose to generate annotations for the whole search result.

The implementation we provide is based on Twitter, as it is the most widely used and biggest microblogging platform, and on Wikipedia. The motivation for choosing Wikipedia as entity source was that it offers a wide coverage of topics. Furthermore, automatic tools for annotating text with Wikipedia entities are readily available (see \cite{key:wikifier}). External data sources also map to DBpedia, thus combined querying of external sources and Twitter search results becomes possible. Note however that a direct mapping of hashtags to entities is not possible in many cases: e.g. there is no entity in DBpedia which describes the European Semantic Web Conference 2011, thus the tag $\#eswc2011$ can not mapped directly.

Annotations should be stable over time, unless the topics discussed in the microblog messages containing the search term change. In an evaluation of our approach we have tried to analyse the stability of the result.

Our contributions thus are:
\begin{itemize}
	\item We present an approach for finding entities which are related to search results on microblogging platforms
	\item We specify a formatting of microblogging messages as RDF
	\item We evaluate the stability of the found entities.
\end{itemize}

The remainder of this paper is organized as follows: in Section~\ref{sect:relWork} we discuss related work, in Section~\ref{sect:method} we present our approach, the results of our evaluation are presented in Section~\ref{sect:eval}, before we conclude in Section~\ref{sect:conclusion}.

@@

The goal of our method is to, given a search query $q$ as input, provide the user with an RDF\footnote{\url{http://www.w3.org/RDF/}} document describing the search result $R$, i.e. the most recent messages that match the query, the authors of these messages and the most relevant entities $E$ for this result. 
In the following we will illustrate our approach based on a search for the hashtag $\#Libya$, a hashtag
which is frequently used to describe posts related to the country of Libya.

@@

\begin{enumerate}
	\item In a first step, the most recent search results $R$ for the query are
	obtained.\newline In our example, calling the Wrapper with query $\#Libya$ will
	return a document containing all most recent Twitter posts whose content
	matched the search string $\#Libya$ and their meta information. 
	\newline
	An example\footnote{\url{http://twitter.com/SenJohnMcCain/statuses/46619460060196865}}
for a single retrieved post is the following:
{\small
\begin{verbatim}
"Arab League calls for no-fly zone in #Libya http://t.co/ZsLNIWa"
\end{verbatim}}
This messageposted by Twitter user \texttt{SenJohnMcCain}; geo coordinates\footnote{The original Twitter message posted by SenJohnMcCain was not geotagged} and the date the message has been posted are furthermore known.

@@

In our example, the message contains a link to
\url{http://t.co/ZsLNIWa}, which redirects to an article on the situation in
Libya published on \url{http://reuters.com}. Dereferencing this URL and grabbing
the text found at the link should return the following text:
{\small\begin{verbatim}"Arab League calls for Libya no-fly zone-state TV - CAIRO, March 12
(Reuters) - The Arab League on Saturday called on the U.N. Security 
Council to impose a no-fly zone on Libya, Egyptian state television
reported, a decision that would give a regional seal of approval
that NATO has said is needed for any military action."\end{verbatim}}
	\item In a third step entities matching the search result are retrieved. The
	content of the Twitter messages that matched the search query and, if available, the content of referenced websites is merged to a single input string and used as input for the annotation. The result of this step is a list of matching articles of the English Wikipedia.

In our example, the contents of all posts related to the search term '\#Libya'
are merged with the retrieved external website content. Thus, the post obtained from
step 1 would be matched with the website content obtained in step 2 into a
single input stream:
\begin{verbatim}"Arab League calls for no-fly zone in #Libya
Arab League calls for Libya no-fly zone-state TV - CAIRO, 
March 12 (Reuters) - The Arab League on Saturday called on the 
U.N. Security Council to impose a no-fly zone on Libya, 
Egyptian state television reported, a decision that would give
a regional seal of approval that NATO has said is needed for 
any military action."\end{verbatim}
This string is appended to the Twitter content and the external content of all other posts in the result.

@@

\section{Implementation}

@@

We have conducted experiments on a set of queries which were identified to be hashtags which are frequently used on Twitter.
To obtain these, we have sampled the Twitter message feed using Twitter's
Streaming API for one minute twice an hour from 2011-03-03 to 2011-03-06. The
top-50 hashtags dervied from the aggregate sample are listed in Table
\ref{tbl:hashtags}, count is the number of times we encountered them during the
collection period.

@@

\begin{table}[ht]
\centering
\small
\begin{tabular}{l|l|l|l}
Hashtag & Extern & $E$ & $sts$ \\%& $E_2$ & $sts(E_2)$ & $E_3$ & $sts(E_3)$ \\
\hline
$\#tilltheworldends$ & false & Britney Spears & .9583 \\
& &  iTunes & .6875 \\
& &  itunes & .625 \\ 
\hline
$\#nowplaying$ & false & iTunes & .5208 \\
& & Michael Jackson & .333 \\
& & Lady Gaga & .333 \\
\hline
$\#nowplaying$ & true & YouTube & .8235 \\
& & Hip Hop Music & .6471 \\
& & The Notorious B.I.G. & .5883 \\
\hline
$\#np$ & false & Chris Brown\_(entertainer) & .5 \\
& & Usher & .3125 \\
& & Lil Wayne & .2917 \\
\hline
$\#np$ & true & Chris Brown\_(entertainer) & .5 \\
& & YouTube & .375 \\
& & Ne-Yo & .315 \\
\hline
$\#thataintwinning$ & false & Mozilla Firefox & .2291 \\
& & Twitter & .2291 \\
& & twitter & .1667 \\
\hline
$\#thataintwinning$ & true & twitter & .5208 \\
& & Twitter & .5 \\
& & Two and a half men & .125 \\
\hline
$\#blackpeoplemovies$ & false & Devil & .4791 \\
& & Tyler Perry & .2708 \\
& & Harry Potter & .2292 \\
\hline
$\#blackpeoplemovies$ & true & Amazon.com & 1 \\
& & YouTube & 1 \\
& & amazon.com & 1
\end{tabular}
\label{tbl:entities}
\caption{Most frequent entities and their single term stabilities}
\end{table}

@@

The third highest stability was achieved by the tag $\#tilltheworldends$ which refers to Britney Spears' newest single. The different spellings of iTunes which are used for annotation occur as the Wikifier does not return normalized entities.

@@

The effect of considering external content in the annotation is beneficial in some cases, in others the effect was destabilizing. The highest decrease in stability was observed for the tag $\#thataintwinning$, the highest increase occured for the tag $\#blackpeoplemovies$. Our hypothesis is that destabilization occurs especially in cases where the posted links cover a variety of topics, while for more specific hashtags referenced web sites are more likely to cover a specific topics and will thus be stabilizing.

@@

The SemanticTweet\footnote{\url{http://semantictweet.com}} service is a tool which allows for the generation of a FOAF file describing one's network of followers and friends on Twitter. Thus, an automatic way of mapping the Twitter social network to semantic data is made available. The transformation is syntactic and does not include links to topics.

@@

Softic et al \cite{key:softic} have developed a framework and system for mining data from social networks. They have instantiated their system to analyse data from Twitter. In their system, they collect data from one or several users. The system by Passant et al. \cite{key:smob} is used for transforming Twitter data to semantic data. The triplified data can then be analysed using SPARQL. They propose that the result data could be enriched using entities from other Linked Open Data vocabularies like dbpedia\footnote{\url{http://dbpedia.org}} or GeoNames\footnote{\url{http://www.geonames.org}}, but they do not provide an actual method how this annotation can be achieved.

@@

\section{Conclusion}
\label{sect:conclusion}

We have presented an approach for annotating search results on microblogging platforms with Wikipedia entities, as well as an implementation and an evaluation of the approach.

Our evaluation has shown that a direct mapping of hashtags to a single dbpedia concept is not possible in many cases. One reason is the use of hashtags in different contexts, another reason is that hashtags do not necessarily describe an entity, but are rather used to describe contexts.

Another difficult problem we encountered is that different languages have to be dealt with: Topics are often commented on in a variety of languages on microblogging platforms. However, NLP techniques which are used to analyse the messages are language dependent.

>>>>

\title{Mapping Microblog Posts to Encyclopedia Articles}
\author{Uta L\"{o}sch \and David M\"{u}ller \and Andreas Harth}
\institute{Institute AIFB, Karlsruhe Institute of Technology (KIT), Germany\\ 
	\email{uta.loesch@kit.edu},\\
	\email{david.mueller@student.kit.edu},\\
	\email{harth@kit.edu}
}
\begin{document}

@@

\begin{abstract}
Microblog posts may contain so-called hashtags that mark keywords or topics.
Hashtags are used in an ad-hoc fashion; the meaning of hashtags is implicitly defined via their use, which makes understanding and querying hashtags difficult.
In this paper we devise a method for annotating microblog posts which contain hashtags with related encyclopedia entities.
% that best describe the hashtag.
Thus, users have the means to quickly grasp the meaning of a hashtag, and gain starting points for further exploration of the hashtags' context.
%By relating the hashtags to external content, users 
We implement two variants of our method based on an existing system for linking content to Wikipedia and analyse the stability of annotated  Twitter search results for popular hashtags.
\end{abstract}

\nop{
Keywords: Twitter, Wikipedia, DBpedia, RDF

http://tagdef.com/ has a list of popular tags
}

@@

Microblogging services allow users to publish short messages online.
Twitter\footnote{\url{http://twitter.com/}} is the largest dedicated microblogging site; as of March 2011, its users create an average of 140 millions post a day\footnote{\url{http://blog.twitter.com/2011/03/numbers.html}}.
Given a 140-character limit for posts, Twitter users invented shortcuts for certain expressions.
So-called hashtags (starting with a \# sign followed by a keyword) are frequently used to associate posts with a specific topic, place, person or event.
For example, posts covering current events in Lybia are frequently tagged with $\#Libya$.
%the Extended Semantic Web Conference 2011 will frequently be tagged with $\#eswc2011$.

Hashtags can help to organise microblog messages and thus are useful for supporting search.
Microblogging platforms offer functionality to search for messages containing a specific hashtag.
%This search returns the most recent messages containing the tag.
However, as hashtags are implicitly defined via their use, the meaning of a hashtag is often unclear.
Services such as tagdef\footnote{\url{http://www.tagdef.com/}} provide means to provide a definition of a hashtag, but these services rely on user input and thus only cover a subset of all hashtags.
In addition, since hashtags are not related to other structured information sources, querying is limited to direct keyword search.

We propose a method to associate hashtags to encyclopedia entities.
In our experiments we use Wikipedia as entity source which covers a wide range of topics.
Furthermore, automatic tools for annotating text with Wikipedia entities are readily available, for example Milne and Witten's Wikifier \cite{key:wikifier}.
Wikipedia entities are widely linked to external data sources via DBpedia \cite{key:dbpedia}, thus combined querying of DBpedia and Twitter becomes possible.

Matching entities in microposts is a difficult problem \cite{key:clef} as microblog post are very short and contain little information.
Our approach uses search results for a given hashtag as input to the entity matching component and returns messages using the hashtag including a set of related Wikipedia entities.
% which have been detected in the search result.
The matched entities not only help to understand the search terms, but also serve as a starting point for refining the search or searching for further information related to the search result.
%These entities will help the user to gain an understanding in which context the hashtag is used and what it may mean.

%with a set of entities which reflect the content of the result feeds.
%, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.
%grasp the context of the results and to get further information on the topic that was searched for.
%To facilitate this putting into context of the search results, 
%Furthermore, this annotation will help to understand hashtags. 
%If users encounter this hashtag and do not understand it, they can search for it on the microblogging platform.
%However, understanding a search result is difficult and time-consuming.

\nop{
Finding entities matching a query, especially a query for a given hashtag is difficult as little context is available due to the short length of each single message.
}

In this paper, we present a method to automatically annotate hashtag search results with encyclopedia entities.
If a hashtag can be associated with an entity with high confidence, the entity can be seen as descriptive for the hashtag.
We envision a system which automatically finds entities equivalent to a hashtag.
%While it would be more interesting to annotate each single microblog message with relevant entities, microblog messages are too short to contain much relevant information which could be used as input for an annotation tool such as the Wikifier \cite{key:wikifier}.
%Thus, we chose to generate annotations for the whole search result. 
%Our implementation is based on Twitter, the most widely used and biggest microblogging platform, and on Wikipedia.
Annotations should be stable over time, unless the topics discussed in the microblog messages containing the search term change.
In an evaluation of our approach we analyse the stability of the results of the entity matching for hashtag search results.

Our contributions thus are:
\begin{itemize}
	\item We present an approach for finding entities which are related to search results on microblogging platforms.
%	\item We specify a formatting of microblogging messages as RDF.
	\item We evaluate the stability of the found entities.
\end{itemize}

The remainder of this paper is organised as follows: Section~\ref{sect:method} overviews the approach,
Section~\ref{sect:impl} presents the implementation,
Section~\ref{sect:eval} covers the results of the evaluation,
Section~\ref{sect:relWork} discusses related work and  Section~\ref{sect:conclusion} concludes.

@@

The goal of our method is, given a search query $q$ as input, to provide the user with an RDF\footnote{\url{http://www.w3.org/RDF/}} document describing the search result $R$, i.e. the most recent messages that match the query, the authors of these messages and the most relevant entities $E$ for this result. 
In the following we will illustrate our approach based on a search for the hashtag $\#Libya$, a hashtag
which is frequently used to describe posts related to the country of Libya.

@@

\begin{enumerate}
	\item In a first step, the most recent search results $R$ for the query are
	obtained.\newline In our example, calling the Wrapper with query $\#Libya$ will
	return a document containing all most recent Twitter posts whose content
	matched the search string $\#Libya$ and their meta information. 
	\newline
	An example\footnote{\url{http://twitter.com/SenJohnMcCain/statuses/46619460060196865}}
for a single retrieved post is the following:
{\small
\begin{verbatim}
"Arab League calls for no-fly zone in #Libya http://t.co/ZsLNIWa"
\end{verbatim}}
This message posted by Twitter user \texttt{SenJohnMcCain}; geo coordinates\footnote{The original Twitter message posted by SenJohnMcCain was not geo-tagged} and the date the message has been posted are furthermore known.

@@

In our example, the message contains a link to
\url{http://t.co/ZsLNIWa}, which redirects to an article on the situation in
Libya published on \url{http://reuters.com/}. Dereferencing this URL and grabbing
the text found at the link should return the following text:
{\small\begin{verbatim}"Arab League calls for Libya no-fly zone-state TV - CAIRO, March 12
(Reuters) - The Arab League on Saturday called on the U.N. Security 
Council to impose a no-fly zone on Libya, Egyptian state television
reported, a decision that would give a regional seal of approval
that NATO has said is needed for any military action."\end{verbatim}}
	\item In a third step entities matching the search result are retrieved. The
	content of the Twitter messages that matched the search query and, if available, the content of referenced websites is merged to a single input string and used as input for the annotation. The result of this step is a list of matching articles of the English Wikipedia.

In our example, the contents of all posts related to the search term '\#Libya'
are merged with the retrieved external website content. Thus, the post obtained from
step 1 would be matched with the website content obtained in step 2 into a
single input stream:
\begin{verbatim}"Arab League calls for no-fly zone in #Libya
Arab League calls for Libya no-fly zone-state TV - CAIRO, 
March 12 (Reuters) - The Arab League on Saturday called on the 
U.N. Security Council to impose a no-fly zone on Libya, 
Egyptian state television reported, a decision that would give
a regional seal of approval that NATO has said is needed for 
any military action."
\end{verbatim}
This string is appended to the Twitter content and the external content of all other posts in the result.

@@

\section{Implementation}
\label{sect:impl}

@@

We have conducted experiments on a set of queries which were identified to be hashtags which are frequently used on Twitter.
To obtain these, we have sampled the Twitter message feed using Twitter's
Streaming API for one minute twice an hour from 2011-03-03 to 2011-03-06. The
top-50 hashtags derived from the aggregate sample are listed in Table
\ref{tbl:hashtags}, count is the number of times we encountered them during the
collection period.

@@

\begin{table}[ht]
\centering
\small
\begin{tabular}{l|l|l|l}
Hashtag & Extern & $E$ & $sts$ \\%& $E_2$ & $sts(E_2)$ & $E_3$ & $sts(E_3)$ \\
\hline
\#tilltheworldends & false & Britney Spears & .9583 \\
& &  iTunes & .6875 \\
& &  itunes & .625 \\ 
\hline
\#nowplaying & false & iTunes & .5208 \\
& & Michael Jackson & .333 \\
& & Lady Gaga & .333 \\
\hline
\#nowplaying & true & YouTube & .8235 \\
& & Hip Hop Music & .6471 \\
& & The Notorious B.I.G. & .5883 \\
\hline
\#np & false & Chris Brown\_(entertainer) & .5 \\
& & Usher & .3125 \\
& & Lil Wayne & .2917 \\
\hline
\#np & true & Chris Brown\_(entertainer) & .5 \\
& & YouTube & .375 \\
& & Ne-Yo & .315 \\
\hline
\#thataintwinning & false & Mozilla Firefox & .2291 \\
& & Twitter & .2291 \\
& & twitter & .1667 \\
\hline
\#thataintwinning & true & twitter & .5208 \\
& & Twitter & .5 \\
& & Two and a half men & .125 \\
\hline
\#blackpeoplemovies & false & Devil & .4791 \\
& & Tyler Perry & .2708 \\
& & Harry Potter & .2292 \\
\hline
\#blackpeoplemovies & true & Amazon.com & 1 \\
& & YouTube & 1 \\
& & amazon.com & 1
\end{tabular}
\label{tbl:entities}
\caption{Most frequent entities and their single term stabilities}
\end{table}

@@

The third highest stability was achieved by the tag $\#tilltheworldends$ which refers to Britney Spears' newest single. The different spellings of iTunes which are used for annotation occur as the Wikifier does not return normalised entities.

@@

The effect of considering external content in the annotation is beneficial in some cases, in others the effect was destabilising. The highest decrease in stability was observed for the tag $\#thataintwinning$, the highest increase occurred for the tag $\#blackpeoplemovies$. Our hypothesis is that de-stabilisation occurs especially in cases where the posted links cover a variety of topics, while for more specific hashtags referenced web sites are more likely to cover a specific topics and will thus be stabilising.

@@

The SemanticTweet\footnote{\url{http://semantictweet.com/}} service is a tool which allows for the generation of a FOAF file describing one's network of followers and friends on Twitter. Thus, an automatic way of mapping the Twitter social network to semantic data is made available. The transformation is syntactic and does not include links to topics.

@@

Softic et al \cite{key:softic} have developed a framework and system for mining data from social networks. They have instantiated their system to analyse data from Twitter. In their system, they collect data from one or several users. The system by Passant et al. \cite{key:smob} is used for transforming Twitter data to semantic data. The triplified data can then be analysed using SPARQL. They propose that the result data could be enriched using entities from other Linked Open Data vocabularies like DBpedia\footnote{\url{http://dbpedia.org/}} or GeoNames\footnote{\url{http://www.geonames.org/}}, but they do not provide an actual method how this annotation can be achieved.

@@

\section{Conclusion and Future Work}
\label{sect:conclusion}

We have presented an approach for annotating Twitter hashtags with Wikipedia entities.
We have described an implementation of two variants of the method and evaluated the approach.

Our evaluation has shown that a direct mapping of hashtags to a single DBpedia concept is not always possible.
One reason is that hashtags do not necessarily describe an entity, but are rather used to describe contexts.
Another reason is the use of hashtags for different entities.
For example, both the hashtags $\#ka$ and $\#karlsruhe$ are frequently used when talking about topics which are related to the city Karlsruhe.
The tag $\#ka$ is however also used to denote the car type Ford Ka.
Thus, when searching for $\#ka$ on a microblogging platform, messages relating to Karlsruhe will be found as well as messages related to Ford Ka.
An approach which aims at finding relevant entities for a given search will have to be able to disambiguate homonym hashtags.
%deal with these problems.

An issue we have encountered is that different languages have to be dealt with: topics are often commented on in a variety of languages, and the built-in language identifiers are often incorrect.
As the entity matching system is language-dependent we would need to include a language detection component in future versions of the system.

%Note however that a direct mapping of hashtags to entities is not possible in many cases: e.g. there is no entity in DBpedia which describes the Extended Semantic Web Conference 2011, thus the tag $\#eswc2011$ can not be mapped directly.
%Additional problems are due to synonyms and homonyms in the set of hashtags that are frequently used.
